\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-07-01 AffineLieAlgebras/InformalNotes/article.tex
All the V.D.'s changes merged, images improved, paper size greatly reduced (to 30 pages).

We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations. In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations used throughout the paper. In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras to illustrate the algorithm. Then we consider the affine Lie algebras with the applications in CFT models (Section \ref{sec:phys-appl}). We conclude the paper with a review of obtained results. Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator
(when it is projected to the subalgebra root space) the injection fan technique can be properly modified.
The result of this modification is that the generalized recurrent relations for anomalous branching
coefficients \eqref{eq:21} is to be formulated in the following form:
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by the roots of $\mathfrak{g}$
orthogonal to the root subsystem of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the coefficient of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the validity of this relation.

In the subsection \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
based on this formula and present some examples.

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}$ that bring the weights of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
The Weyl-Kac character formula leads to
the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important that the ion of some of positive roots of
the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections
corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
$W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots of the subalgebra
$\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they
are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.

Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root
system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ . This root system
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty
and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
it is clear that $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings are constructed by the exclusion of one or two roots
from the extended Dynkin diagram of the algebra. Since this process can give us
non-connected Dynkin diagrams we can see which roots are orthogonal to the root
space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.

Consider for instance the regular embedding of $A_1\subset B_2$.
The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

The simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular
embedding $\mathfrak{a}\subset \mathfrak{g}$
when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple can be formulated
as follows:
if the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected
diagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
then the subset $\Delta_{\bot}$ is non-empty,
subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the
$\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Notice that when we study the regular embedding obtained by dropping the nodes
of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
subalgebra $\mathfrak{a}$ is one of the connected components,
the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
generated by the remaining connected components.
Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
In this case by eliminating
the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to
$A_1\oplus A_1$ but to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
 Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$. Consider the remaining diagram. This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them. The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$. Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.

All the cases are listed in the table \ref{tab:diagrams}.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}

For the algebra $\mathfrak{g}$ from the series $A_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r+1\}$ are $\Delta=\{\alpha_{ i j}= e_i- e_j,\; 1\leq i, j\leq r+1\}$, $\Delta^{+}=\{\alpha_{ij},\; i<j\}$ and the set of simple roots consists of $\alpha_{1,2},\alpha_{2,3},\dots,\alpha_{r,r+1}$. So for the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consisting of first $r_{\mathfrak{a}}$ simple roots we get $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{ i j},\; r_{\mathfrak{a}}+1<i,j\leq r+1\}$ and $\mathfrak{a}_{\bot}=A_{r-r_{\mathfrak{a}}-1}$.

For the algebra $\mathfrak{g}$ from the series $B_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$. So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}-1}$. Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping the single node from the extended Dynkin diagram of $B_r$. This can be done by choosing the set of simple roots of $\mathfrak{a}$ in the form $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$. Then $\mathfrak{a}=D_{r_{\mathfrak{a}}}$, $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.

>>>>

We demonstrate that our algorithm can be used in studies of conformal embeddings and coset constructions in rational conformal field theory.

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations. In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules $L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$ (subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in CFT models are considered in Section \ref{sec:phys-appl}. We conclude the paper with a review of obtained results. Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ),

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
(when it is projected to the $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
The result is the generalized recurrent relation for anomalous branching
coefficients \eqref{eq:21}:
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
orthogonal $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the multiplicity of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the relation \eqref{eq:1}.

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
The Weyl-Kac character formula leads to
the relation
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important whether there exist the positive roots $\alpha\in \Delta$ such that $\pi_{\mathfrak{a}}\alpha=0$. These roots are orthogonal to $P_{\mathfrak{a}}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the Weyl reflections
corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
$W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots $\beta\in \Delta_{\mathfrak{a}}$ are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
So the subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$.

Thus we have obtained the system $\Delta_{\bot}$ orthogonal $P_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$. It
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty with the non-trivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then $r_{\mathfrak{a}}=r$ and
 $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings can be described by the elimination of one or two roots
from the extended Dynkin diagram of the algebra. When the process gives us
non-connected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.  The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.

For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be nontrivial can be formulated as follows:
if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
then the subset $\Delta_{\bot}$ is non-empty,
subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and
$\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Notice that when we study the regular embedding obtained by dropping the nodes
of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
subalgebra $\mathfrak{a}$ is one of the connected components,
the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
generated by the remaining connected components of the diagram.
Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
In this case by eliminating
the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
 Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$. The remaining diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ with $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\mathfrak{\bar{a}}$ but the linear combinations of them. The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$. Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$. 
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
\begin{equation}
  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
\end{equation}
Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
and take into account that the projection commutes with the multiplication:
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{multline}
Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and simplify the first factor,
\begin{multline}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{multline}
